---
title: "iteration_and_listcols"
author: "Eric Morris"
date: "10/30/2018"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(rvest)

```

## Lists

```{r}
l = list(vec_numeric = 5:8,
         mat         = matrix(1:8, 2, 4),
         vec_logical = c(TRUE, FALSE),
         summary     = summary(rnorm(1000)))
l
```


## For Loops

```{r}
df = data_frame(
  a = rnorm(20, 3, 1),
  b = rnorm(20, 0, 5),
  c = rnorm(20, 10, .2),
  d = rnorm(20, -3, 1)
)

is.list(df)

df[[2]]
```

Function from last class:

```{r}
mean_and_sd = function(x) {
  
  if (!is.numeric(x)) {
    stop("Argument x should be numeric")
  } else if (length(x) == 1) {
    stop("Cannot be computed for length 1 vectors")
  }
  
  mean_x = mean(x)
  sd_x = sd(x)

  tibble(
    mean = mean_x, 
    sd = sd_x
  )
}
```

We can apply the function to our df

```{r}
mean_and_sd(df[[1]])
mean_and_sd(df[[2]])
mean_and_sd(df[[3]])
mean_and_sd(df[[4]])
```

Writing a for loop:

```{r}
output = vector("list", length = 4)

for (i in 1:4) {
  
  output[[i]] = mean_and_sd(df[[i]])
  
}

output
```

## Map Statements

Let's replace the for loop with map 

```{r}
output = map(df, mean_and_sd)

output
```

Let's try a different function

```{r}
output = map(df, median)
output = map(df, summary)
```


## Map variant

```{r}
output = map_df(df, mean_and_sd)

output = map_dbl(df, median)
```


## Code Syntax

Being clear about arguments and inputs to avoid confusion

```{r}
output = map( .x = df, ~mean_and_sd(x = .x, na.rm = FALSE))
```

2 inputs into map function, LOTR code below won't work since haven't specified x and y

```{r}
lotr_data = map2_df(
  .x = cell_ranges, .y = movie_names, 
  ~lotr_load_and_tidy(path = "./data/LotR_Words.xlsx", range = .x, movie_name = .y))

```

## Learning assessment 

```{r}
read_page_reviews <- function(url) {
  
  h = read_html(url)
  
  title = h %>%
    html_nodes("#cm_cr-review_list .review-title") %>%
    html_text()
  
  stars = h %>%
    html_nodes("#cm_cr-review_list .review-rating") %>%
    html_text() %>%
    str_extract("\\d") %>%
    as.numeric()
  
  text = h %>%
    html_nodes(".review-data:nth-child(4)") %>%
    html_text()
  
  data_frame(title, stars, text)
}

url_base = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber="
vec_urls = str_c(url_base, 1:5)


read_page_reviews(vec_urls[[1]])

# map to do this 

reviews = map(vec_urls, read_page_reviews)
reviews

dynamite_reviews = map_df(vec_urls, read_page_reviews)

# forloop

dyn_output = vector(vec_urls, length = 5)

for (i in 1:5) {
  
  output[[i]] = read_page_reviews(df[[i]])
  
}

dyn_output
```

## Weather

```{r}
library(rnoaa)

weather = 
  meteo_pull_monitors(c("USW00094728", "USC00519397", "USS0023B17S"),
                      var = c("PRCP", "TMIN", "TMAX"), 
                      date_min = "2016-01-01",
                      date_max = "2016-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY", 
                      USC00519397 = "Waikiki_HA",
                      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

```{r}
weather_nest = 
  weather %>% 
  nest(date:tmin)

#alt: weather_nest = weather %>% group_by(name, id) %>% nest

weather_nest %>% 
  pull(name)

weather_nest %>% 
  pull(id)

weather_nest %>% 
  pull(data)
```

Unnesting .. 

```{r}
weather_nest %>% 
  unnest()
```

Look at list col elements

```{r}
weather_nest$data[[1]] %>% 
  skimr::skim()
```

Fit a location-specific regression

```{r}
lm(tmax ~ tmin, data = weather_nest$data[[1]]) #CP

lm(tmax ~ tmin, data = weather_nest$data[[2]]) #Waikiki

lm(tmax ~ tmin, data = weather_nest$data[[3]]) #Waterhole
```

Write a function dummy!

```{r}
weather_lm = function(df){
  
  lm(tmax ~ tmin, data = df)
  
}
```

```{r}
weather_lm(df = weather_nest$data[[1]]) #checking this works
```


```{r}
map(weather_nest$data, weather_lm)
```

Save this ouput as a new list column in the og df

```{r}
weather_nest %>% 
  mutate(lm_results = map(data, weather_lm))
```

