---
title: "writing_functions"
author: "Eric Morris"
date: "10/25/2018"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

knitr::opts_chunk$set(
  collapse = TRUE,
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
library(tidyverse)
library(rvest)
theme_set(theme_bw() + theme(legend.position = "bottom"))
```

## Writing some functions 

Starting smol

```{r}
x = rnorm(25, 5, 3)

(x - mean(x)) / sd(x)
```

Write a function to compute z scores for a vector

```{r}
z_scores = function(x) {
  
  (x - mean(x)) / sd(x)
  
}
```

Check to see if this works 

```{r}
unif_sample = runif(100)

z_scores(x = unif_sample)
```

Check some other examples

```{r, error = TRUE}
z_scores(3)
z_scores("my name is jeff")
z_scores(iris)
z_scores(sample(c(TRUE, FALSE), 25, replace = TRUE))
```

Put in some checks on inputs for your function...

```{r}
z_scores = function(x) {
  
  if (!is.numeric(x)) {
    stop("Argument x should be numeric")
  } else if (length(x) == 1) {
    stop("Z scores cannot be computed for length 1 vectors")
  }
  
  z = mean(x) / sd(x)
  
  z
}
```

## New function for mean and SD

```{r}
mean_and_sd = function(x) {

  if (!is.numeric(x)) {
    stop("Argument x should be numeric")
  } else if (length(x) == 1) {
    stop("Z scores cannot be computed for length 1 vectors")
  }
  
  tibble(
  mean_x = mean(x),
  sd_x = sd(x)
  )
  
  #c(mean_x, sd_x) 
  
}

mean_and_sd(unif_sample)

```


## Multiple inputs

Look at simple linear regression! 

```{r}
sim_data = tibble(
  x = rnorm(30, 1, 1),
  y = 2 + 3 * x + rnorm(30, 0, 1)
)

# sim_data %>% ggplot(aes(x = x, y = y)) + geom_point()

ls_fit = lm(y ~ x, data = sim_data)

beta0_hat = coef(ls_fit)[1]
beta1_hat = coef(ls_fit)[2]

```


Write a function that simulates data, fits the model, and returns the estimates. Inputs are sample size and true coefficients 


```{r}
sim_regression = function(n, beta0, beta1) {
  sim_data = tibble(
    x = rnorm(n, 1, 1),
    y = beta0 + beta1 * x + rnorm(n, 0, 1)
  )

  ls_fit = lm(y ~ x, data = sim_data)
  
  tibble(
    beta0_hat = coef(ls_fit)[1],
    beta1_hat = coef(ls_fit)[2]
  )

}
```

Running the sim:

```{r}
sim_regression(n = 30, beta0 = 2, beta1 = 5)

sim_regression(n = 3000, beta0 = 0, beta1 = -1)

```


## More functions!!11!!! and some old examples

Writing a function to extract amazon reviews instead of the old code we had 

```{r}
url = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber=1"

extract_reviews = function(url) {
  
  dynamite_html = read_html(url)
  
  review_titles = dynamite_html %>%
    html_nodes("#cm_cr-review_list .review-title") %>%
    html_text()
  
  review_stars = dynamite_html %>%
    html_nodes("#cm_cr-review_list .review-rating") %>%
    html_text() %>%
    str_extract("\\d") %>%
    as.numeric()
  
  review_text = dynamite_html %>%
    html_nodes(".review-data:nth-child(4)") %>%
    html_text()
  
  reviews = tibble(
    title = review_titles,
    stars = review_stars,
    text = review_text
  )
  reviews
}

extract_reviews(url)
```

Let's extract a lot of reviews...

```{r}
url_base = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber="
urls = str_c(url_base, 1:5)

dynamite_reviews = bind_rows(
  extract_reviews(urls[1]),
  extract_reviews(urls[2]),
  extract_reviews(urls[3]),
  extract_reviews(urls[4]),
  extract_reviews(urls[5])
)
dynamite_reviews
```


LOTR Function

```{r}
fellowship_ring = readxl::read_excel("./data/LotR_Words.xlsx", range = "B3:D6") %>%
  mutate(movie = "fellowship_ring")

two_towers = readxl::read_excel("./data/LotR_Words.xlsx", range = "F3:H6") %>%
  mutate(movie = "two_towers")

return_king = readxl::read_excel("./data/LotR_Words.xlsx", range = "J3:L6") %>%
  mutate(movie = "return_king")

lotr_tidy = bind_rows(fellowship_ring, two_towers, return_king) %>%
  janitor::clean_names() %>%
  gather(key = sex, value = words, female:male) %>%
  mutate(race = tolower(race)) %>% 
  select(movie, everything()) 
```


```{r}
lotr_load_and_tidy = function(range, title){
  
  readxl::read_excel("./data/LotR_Words.xlsx", range = range) %>%
    mutate(movie = title) 
  
}

lotr = lotr_load_and_tidy(range = "B3:D6", title = "fellowship")
lotr 
```


## Scoping

```{r}
f = function(x) {
  z = x + y
  z
}

x = 1
y = 2

f(x = y)
```

